Computing in the Field of Rationals

### 2012-06-25 rational_ext.tex
_

These negative and fractional dualities must not confused with
$(\-)^\bot$ duality in the additive and multiplicative fragment of
linear logic.  Models of linear logic rely on *-autonomous categories
which change the monoidal tensor when dualizing. Compact closed
categories preserve the monoidal tensor on dualizing.  The term model
of {{PiEE}} corresponds to the \emph{categorification of a field}. The
category is compact closed over the additive monoid. In the
multiplicative monoid, since there is no division by zero, respects
compact closed structure only when a dual object is defined.

The types of {{PiEE}} correspond to the \emph{field of rational
  numbers} (with the important restriction of fields that there is no
division by zero). Consequently algebraic manipulations of rationals
can be given an operational interpretation and \emph{have
  computational content}.

>>>>

The types of {{PiEE}} correspond to the \emph{field of rational
  numbers} (with the important restriction of fields that there is no
division by zero). Consequently algebraic manipulations of rationals
can be given an operational interpretation and \emph{have
  computational content}.  These negative and fractional dualities
must not confused with $(\-)^\bot$ duality in the additive and
multiplicative fragment of linear logic.  Models of linear logic rely
on *-autonomous categories which change the monoidal tensor when
dualizing. Compact closed categories preserve the monoidal tensor on
dualizing.  The term model of {{PiEE}} corresponds to the
\emph{categorification of a field}. The category is compact closed
over the additive monoid. In the multiplicative monoid (since there is
no division by zero) respects compact closed structure only when a
dual object is defined.
